A linearization procedure for constrained multibody systems

### 2012-10-03 PetersonGedeHubbard2012.tex
Fixed spelling error.
Changed .pgf figure to pdf and updated .tex file accordingly.

\usepackage{graphicx}
\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{pgf}
%\usepackage[polutonikogreek]{babel}

@@

\begin{abstract}
% Context
Many common mechanical systems have configuration or velocity constraints.
% Need  (what we have and what we want)
Analyses of such systems often require linearized forms of the motion
equations.  Although derivation of the nonlinear motion equations is well
understood, very little has been presented on the proper approach to
forming linearized versions which satisfy the constraints.
% Task
To address this issue, we developed a procedure for organizing the constraints
and motion equations, and subsequently linearizing these equations.
% Object of the document
In this paper we present this procedure to linearize the nonlinear motion
equations of constrained multibody systems, and illustrate it with a familiar
example, the rolling disc.
% Findings
We apply this procedure to a model of a bicycle that includes a closed
kinematic loop and four nonholonomic constraints and find that the resulting
symbolic linearized motion equations are identical to previously published
results.  The technique can be performed symbolically (enabling explict
analytical forms of the linearized dynamics) or numerically.
% Conclusion
Motion equations for constrained multibody systems can now be linearized in a
systematic fashion, symbolically or numerically, thereby facilitating common
linear analyses (e.g., stability analysis and control system design).
% Perspectives
Efficiency of computer implementations of this procedure will be considered in
future studies.
\keywords{symbolic dynamics, control, constrained multibody systems}
\end{abstract}

@@

\begin{figure}
  \centering
  \input{rollingdisc.pgf}
  \caption{Rolling disc configuration}
  \label{fig:disc}
\end{figure}

@@

With this example, we have used our linearization procedure to find linear
equations of motion, which respect the system's constraints. Parametric
stability analysis (eigenvalue analysis) can now be performed on these equations.
These computations were implemented symbolically with the open source symbolic
manipulator SymPy \cite{SymPy2012}.

>>>>

\usepackage{graphicx}
\usepackage[fleqn]{amsmath}
\usepackage{amssymb}
\usepackage{bm}
%\usepackage{pgf}
%\usepackage[polutonikogreek]{babel}

@@

\begin{abstract}
% Context
Many common mechanical systems have configuration or velocity constraints.
% Need  (what we have and what we want)
Analyses of such systems often require linearized forms of the motion
equations.  Although derivation of the nonlinear motion equations is well
understood, very little has been presented on the proper approach to
forming linearized versions which satisfy the constraints.
% Task
To address this issue, we developed a procedure for organizing the constraints
and motion equations, and subsequently linearizing these equations.
% Object of the document
In this paper we present this procedure to linearize the nonlinear motion
equations of constrained multibody systems, and illustrate it with a familiar
example, the rolling disc.
% Findings
We apply this procedure to a model of a bicycle that includes a closed
kinematic loop and four nonholonomic constraints and find that the resulting
symbolic linearized motion equations are identical to previously published
results.  The technique can be performed symbolically (enabling explicit
analytical forms of the linearized dynamics) or numerically.
% Conclusion
Motion equations for constrained multibody systems can now be linearized in a
systematic fashion, symbolically or numerically, thereby facilitating common
linear analyses (e.g., stability analysis and control system design).
% Perspectives
Efficiency of computer implementations of this procedure will be considered in
future studies.
\keywords{linearization, constrained multibody systems, symbolic dynamics, control}
\end{abstract}

@@

\begin{figure}
  \centering
  \includegraphics{rollingdisc.pdf}
  \caption{Rolling disc configuration}
  \label{fig:disc}
\end{figure}

@@

With this example, we have used our linearization procedure to find linear
equations of motion which respect the system's constraints. Parametric
stability analysis (eigenvalue analysis) can now be performed on these
equations.  These computations were implemented symbolically with the open
source symbolic manipulator SymPy \cite{SymPy2012}.
